\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-03-04 paper/main.tex
.

\begin{figure}[!tpb]
	\centerline{\includegraphics[width=0.45\textwidth]{figures/full_model.png}}
	\caption{Full DTI prediction model based on the pretrained learnable feature transformations (LFT) for either molecular structure or ontology based features. The transformed protein representations are added to each corresponded protein as node features for the graph convolutional steps. }
	\label{fig:Fullmodel}
\end{figure}

@@

We first perform a cross-validation over proteins and validate our
results. Cross-validation over proteins aims to evaluate how the model
performs when tasked to identify drugs that may target a ``novel''
protein, i.e., one not seen during training.
\todo[inline]{Describe/add the CV results here.}

Second, we use the model trained on STITCH and evaluate the model on
the Yamanishi benchmark dataset\todo{This needs another sentence
  stating how you made sure there was no overlap in data.}.

>>>>

\begin{figure}[!tpb]
	\centerline{\includegraphics[width=0.45\textwidth]{figures/full_model.png}}
	\caption{Full DTI prediction model based on the pretrained
          learnable feature transformations (LFT) for either molecular
          structure or ontology based features. The transformed
          protein representations are added to each corresponded
          protein as node features for the graph convolutional
          steps.}
	\label{fig:Fullmodel}
\end{figure}

@@

We evaluate our model's ability to identify drug--target interactions
using different approaches and datasets.  First, we perform a
cross-validation over proteins and validate our results. A
cross-validation over proteins aims to evaluate how the model performs
when tasked to identify drugs that may target a ``novel'' protein,
i.e., one not seen during training, or a protein for which a drug that
targets it should be predicted.  \todo[inline]{Describe/add the CV
  results here.}

Our model is trained on the STITCH database. We use the model trained
on STITCH and evaluate the model on the Yamanishi benchmark
dataset\todo{This needs another sentence stating how you made sure
  there was no overlap in data.}.
